---
title: "final project-Word prediction"
author: "saeed"
date: "18/04/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## Introduction

The goal of this exercise is to create a product to highlight the prediction algorithm that you have built and to provide an interface that can be accessed by others. For this project you must submit:

A Shiny app that takes as input a phrase (multiple words) in a text box input and outputs a prediction of the next word.
A slide deck consisting of no more than 5 slides created with R Studio Presenter (https://support.rstudio.com/hc/en-us/articles/200486468-Authoring-R-Presentations) pitching your algorithm and app as if you were presenting to your boss or an investor.

## Creating the Model

To create the prediction app I started using the data provided by coursera [Data](https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip), and doing some preprocessing on data such as removing punctuations and numbers. After that I used NLP to create the model aka tokenizing the data.

### Prediction

To predict the next word the app will get a phrase from the user and based on the number of words entered it will use NLP algorithm and gives a result. there is an slider on the side of app to let the user choose how many words to be predicted to maximum of 5 words. There is aslo a checkbox to let the user check the frequency of possible next word.

## Shiny App

Below is a picture of the shiny App created for this project.

```{r,echo=FALSE, out.width="100%"}
knitr::include_graphics("C:/Users/S.kh/Pictures/Screenshots/Screenshot (4).png")
```

## Links

--[ShinyApp](https://saeedk.shinyapps.io/wordpredict/)


--[github](https://github.com/vyn66/Data-Science-Capstone)
